### 2021-07-21 paper/paper.tex
first brief description of PID results

@@

        % \node at (axis cs:10,0.6) {Will be improved soon};
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
\end{figure}

>>>>

The results of this comparison are visualized in Figure~\ref{fig:PID-Euler}.
Clearly, Trixi.jl is a bit more than 2x faster than the Fortran code FLUXO
while both implement the same numerical methods. This demonstrates the
suitability of Julia for this kind of simulation-focused scientific computing.

Note that we do not want to state that Julia is generically faster than Fortran,
C, or C++. In contrast, we would like to emphasize that Julia can be at least
as fast as code written in these traditional scientific computing languages.
We believe that it will be possible to get the same efficiency by rewriting
FLUXO appropriately. However, the code introspection and profiling tools available
in Julia make it easier for us to optimize Julia code compared to other languages
we are familiar with (having a diverse team with a strong background in C, C++,
and Fortran).

@@

        % \node at (axis cs:10,0.6) {Will be improved soon};
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}
